Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
Oops
Ana

\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, North Korea}

@@

\author{Ana Oprescu}
\affiliation{\institution{University of Amsterdam}}
\email{ana.oprescu@uva.nl}

@@

We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones improve system design and thus should be refactored. We evaluate our approach over a large corpus of open source Java projects.

>>>>

\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}

@@

\author{Ana Oprescu}
\affiliation{\institution{University of Amsterdam}}
\email{a.m.oprescu@uva.nl}

@@

We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones improve system design when refactored. We evaluate our approach over a large corpus of open source Java projects.
